---
title: "p8105_hw1_jt3387"
output: github_document
date: "2022-09-22"
---

```{r message =  FALSE}
library(tibble)
library(tidyverse)
library(ggplot2)
```

## Problem 1

Load `penguins` dataset and clean up the column names.

```{r}
data("penguins", package = "palmerpenguins")
penguins <- janitor::clean_names(penguins)
```

Description of the `penguins` dataset:  

- The names of the variables: *``r names(penguins)``*.
- The values of important variables: *``r names(penguins)[1]``*:``r levels(penguins$species)``; 
                                     *``r names(penguins)[2]``*:``r levels(penguins$island)``;
                                     *``r names(penguins)[7]``*:``r levels(penguins$sex)``;
                                     *``r names(penguins)[8]``*:``r unique(penguins$year)``.
- The size of the dataset:  ``r nrow(penguins)`` rows and ``r ncol(penguins)`` columns.
- The mean flipper length: ``r mean(pull(penguins, "flipper_length_mm"), na.rm = TRUE)`` mm.

Make a scatterplot of `flipper_length_mm` (y) vs `bill_length_mm` (x).

```{r warning=FALSE}
ggplot(penguins, aes(y = bill_length_mm, x = flipper_length_mm, color = species)) + geom_point()
```

Export the scatterplot to project directory.

```{r warning=FALSE,message=FALSE}
ggsave("penguins_scatterplot.png")
```

## Problem 2

Create a data frame.

```{r}
set.seed(777)
dataframe <-  tibble(
  vec_numeric <- rnorm(10),
  vec_logic <- c(vec_numeric > 0),
  vec_character <- vector("character", length = 10),
  vec_factor <- factor(c("a", "a", "a", "b", "b", "b", "b", "c", "c", "c"))
)
```

Calculate the mean of each variable.

```{r warning=FALSE}
for (i in 1:4) {
 cat(mean(pull(dataframe, names(dataframe)[i])), "\n")
}
```

The result shows that the numeric and logical variables' mean can be calculated, while the character and factor variables' mean can't be.
