---
title: "p8105_hw1_jt3387"
output: github_document
date: "2022-09-22"
---

```{r message =  FALSE}
library(tibble)
library(tidyverse)
library(ggplot2)
```

## Problem 1

Load `penguins` dataset.

```{r}
data("penguins", package = "palmerpenguins")
```

Description of the `penguins` dataset:  

- The names of the variables: *``r names(penguins)``*.
- The values of important variables: *``r names(penguins)[1]``*:``r levels(penguins$species)``; 
                                     *``r names(penguins)[2]``*:``r levels(penguins$island)``;
                                     *``r names(penguins)[7]``*:``r levels(penguins$sex)``;
                                     *``r names(penguins)[8]``*:``r unique(penguins$year)``.
- The size of the dataset:  ``r nrow(penguins)`` rows and ``r ncol(penguins)`` columns.
- The mean flipper length: ``r mean(pull(penguins, "flipper_length_mm"), na.rm = TRUE)`` mm.

Make a scatterplot of `flipper_length_mm` (y) vs `bill_length_mm` (x)

```{r warning=FALSE}
ggplot(penguins, aes(y = bill_length_mm, x = flipper_length_mm, color = species)) + geom_point()
```
